\ifdefined\MAINTEXT \else Supplemental Material: \\ \fi Low-cost linear-scaling \emph{ab initio} molecular dynamics for weakly-interacting systems

### 2017-11-21 almo-langevin.tex
Dispersion-corrected XC
Updated MSD and diffusion constants.

To test the accuracy of ALMO AIMD we used trajectory analyzer TRAVIS~\cite{a:travis-main} to compute the infrared (IR) spectrum, RDF, and diffusion coefficient of liquid water from both the ALMO trajectory ($\epsilon_{\text{SCF}} = 10^{-2}$~a.u. and $R_{c} = 1.6$ vdWR) and from the reference trajectory. 
The diffusion coefficients $D_{\text{OT}}=\SI{5.47e-9}{\m^{2}\cdot\s^{-1}}$ and $D_{\text{ALMO}}=\SI{5.55E-09}{\m^{2}\cdot\s^{-1}}$ and RDFs (Figure~\ref{fig:dynproperties}a) are in perfect agreement. The quality of the ALMO IR spectrum (Figure~\ref{fig:dynproperties}c) is good despite minor errors in the intensity of the OH stretching mode, which is sensitive to the precise positions of the centers of localized orbitals. These stringent tests show that despite noticeable errors in the ALMO forces (Figure \ref{fig:randomforce}a) the compensating $R^{\Delta}(t)$ term in the modified Langevin equation makes it possible to recover atomic dynamics properly. We would like to note that ALMO AIMD could not be stabilized with $\Delta=0$. Neither we were able to find any values of $\Delta$ that stabilize trajectories generated using perturbative versions of ALMO DFT~\cite{a:almo-ls}.

>>>>

To test the accuracy of ALMO AIMD we used trajectory analyzer TRAVIS~\cite{a:travis-main} to compute the infrared (IR) spectrum, RDF, and diffusion coefficient of liquid water from both the ALMO trajectory ($\epsilon_{\text{SCF}} = 10^{-2}$~a.u. and $R_{c} = 1.6$ vdWR) and from the reference trajectory. 
The diffusion coefficients $D_{\text{OT}}=\SI{4.61E-10}{\m^{2}\cdot\s^{-1}}$ and $D_{\text{ALMO}}=\SI{3.19E-10}{\m^{2}\cdot\s^{-1}}$ and RDFs (Figure~\ref{fig:dynproperties}a) are in good agreement. The quality of the ALMO IR spectrum (Figure~\ref{fig:dynproperties}c) is good despite minor errors in the intensity of the OH stretching mode, which is sensitive to the precise positions of the centers of localized orbitals. These stringent tests show that despite noticeable errors in the ALMO forces (Figure \ref{fig:randomforce}a) the compensating $R^{\Delta}(t)$ term in the modified Langevin equation makes it possible to recover atomic dynamics properly. We would like to note that ALMO AIMD could not be stabilized with $\Delta=0$. Neither we were able to find any values of $\Delta$ that stabilize trajectories generated using perturbative versions of ALMO DFT~\cite{a:almo-ls}.
